Proposed Solution

### 2016-01-29 motiv1.tex

When writing configuration files, the user usually takes already existing files and modifies the, with little knowledge of the system. 
The non-expert user can then easily introduce in errors.
Even worse, the original file may already corrupted and the errors are propagated further. 
Below we show some examples of the errors commonly found in configuration files.
All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
The deep, domain specifc knowledge needed to indentify these error manually is strong motivation for a tool such as \app.

>>>>

When writing configuration files, the user usually takes already existing files and modifies the, with little knowledge of the system. 
The non-expert user can then easily introduce in errors.
Even worse, the original file may already corrupted and the errors are propagated further. 
Below we show some real worlds examples of the errors commonly found in configuration files.
All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
